DRAFT: Week 3: Degree and Centrality

### 2022-03-04 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.2.22 I'm not sure what day it is, and does it really matter?

# Week 2: Scripts
## Smuggler's Index: Network Attributes

@@

Names
- Vertex Names: view
- Edge Attribute Names: [1] "ingTyp"
```{r igraph: Network Description, echo=TRUE}

summary(igEL)
#     Count Vertices
    vcount(igEL)

#     Count Edges
    ecount(igEL)

@@

@@

```{r igraph: Vertex & Attribute info, echo=TRUE}
library(igraph)

#     access vertex attribute 
  head(V(igEL)$name,20)
#     Generate a list the names of vertex attributes
  print(igraph::vertex_attr_names(igEL))

@@

#   Generate a list the names of edge attributes  
  igraph::edge_attr_names(igEL)

#   summarize numeric network attribute
  summary(E(igEL)$weight)

@@

```{r statnet: Network Summary & Attribute info, echo=TRUE}

summary(snEL)
print(snEL)
#     access vertex attributes
 head(snEL %v% "vertex.names")

#      list the names of vertex attributes
  network::list.vertex.attributes(snEL)

#     access edge attribute
  head(snEL%e% "ingTyp")

#  Generate a list the names of edge attributes
  network::list.edge.attributes(snEL)

#   summarize numeric network attribute
  summary(snEL  %v% "name")

@@

dyad.census(igEL)

@@

```{r statnet: Dyad Census , echo=TRUE}
library(statnet)

  sna::dyad.census(snEL)

@@

>>>>

# Week 2: Scripts
## Smuggler's Index: Network Attributes 
```{r Network Size}

  print(snEL)
  print(igEL)

  summary(snEL)
  summary(igEL)

@@

Names
- Vertex Names: view
- Edge Attribute Names: [1] "ingTyp"
```{r igraph: Network & Attribute Descripions, echo=TRUE}

## Network Size
#     Count Vertices
    vcount(igEL)
#     Count Edges
    ecount(igEL)

## Network Attributes

@@

# vertex attribute names
  igraph::vertex_attr_names(igEL)

#   edge attributes  names
  igraph::edge_attr_names(igEL)

#   summarize numeric network attribute
#**summary(E(igEL)$weight)*

@@

```{r igraph: Vetex & Edge Names, echo=TRUE}
library(igraph)

#     access vertex attribute 
  head(
    V(igEL)$name,20)

@@

@@

```{r statnet: Network Summary & Attribute info, echo=TRUE}
print(snEL)

print(summary(snEL))

#      list the names of vertex attributes
  network::list.vertex.attributes(snEL)
#  Generate a list the names of edge attributes
  network::list.edge.attributes(snEL)

#   summarize numeric network attribute
  summary(snEL%v%"name")
  summary(snEL%v%"ingNam")
  summary(snEL%v%"dnkNam")
  summary(snEL%e%"ingTyp")

#     access vertex & edge attribute names
 head(snEL %v% "vertex.names")
#     access edge attribute
  head(snEL%e%"ingTyp")

@@

dyad.census(igEL)
print("Undirected graph, $asym is 0")

@@

```{r statnet: Dyad Census , echo=TRUE}
library(statnet)
library(sna)

    sna::dyad.census(snEL)
  print("statnet thinks it's an undirected network, so there are no mutual ties because it's an undirected network and the 'names' and 'ingredients' in a recipie do not have a reciprocal relationship. If anything the 'flow of info' moves from 'Drink Name' to 'Drink Ingredient' to 'Ingredient type'. The Drink name determines the recipie ingredients, but we're unable to identify a drink by calling on individual ingredients in a recipie")

@@

gplot(sna::dyad.census(snEL))
